---
title: "HW3"
author: "Qiuying Li UNI ql2280"
date: "9/28/2017"
output: word_document
---
1. Consider the Boston dataset, in R library MASS, on Housing Values in Suburbs of Boston
Fit a multiple linear regression model to predict medv (median value of owner-occupied homes in $1000s) using the following set of predictors:

```{r}
library("MASS", lib.loc="/Library/Frameworks/R.framework/Versions/3.3/Resources/library")
data = Boston
lm = lm(medv ~ crim+zn+indus+nox+rm+age+tax, data)
summary(lm)
par(mfrow=c(2,2))
plot(lm)
```
2. State and assess the validity of the underlying assumptions, and suggest remedial measures in case of violations of any of the underlying assumptions
#Linearity/functional form
```{r}
#(a)Check matrix scatter plot
pairs(medv ~crim+zn+indus+nox+rm+age+tax, data)
#(b)Check linearity of each predictor
lm1 = lm(medv~crim,data)
lm2 = lm(medv~zn,data)
lm3 = lm(medv~indus,data)
lm4 = lm(medv~nox,data)
lm5 = lm(medv~rm,data)
lm6 = lm(medv~age,data)
lm7 = lm(medv~tax,data)
par(mfrow = c(2,3))
plot(data$crim,data$medv, main = "medv ~ crim", xlab = "crim", ylab = "medv")
abline(lm1, col = "red")
plot(data$zn,data$medv, main = "medv ~ zn", xlab = "zn", ylab = "medv")
abline(lm2, col = "red")
plot(data$indus,data$medv, main = "medv ~ indus", xlab = "indus", ylab = "medv")
abline(lm3, col = "red")
plot(data$nox,data$medv, main = "medv ~ nox", xlab = "nox", ylab = "medv")
abline(lm4, col = "red")
plot(data$rm,data$medv, main = "medv ~ rm", xlab = "rm", ylab = "medv")
abline(lm5, col = "red")
plot(data$age,data$medv, main = "medv ~ age", xlab = "age", ylab = "medv")
abline(lm6, col = "red")
plot(data$tax,data$medv, main = "medv ~ tax", xlab = "tax", ylab = "medv")
abline(lm7, col = "red")
#(c)Check fitted value V.S. residuals
plot(lm$fitted.values,lm$residuals)
#(d) Check the R^squared
summary(lm)

```
Check Normality
```{r}
#（a) check histogram
hist(lm$residuals, xlab = "residuals", main = "Histogram of residuals")
abline(density(lm$residuals),col = "red")
#(b) check QQ-PLOT
qqnorm(lm$residuals, main = "Normal Q-Q Plot",
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(lm$residuals)
# DO shapiro test
shapiro.test(lm$residuals)
```
#Homoscedasticity
```{r}
#(a) Check the residuals scatterplot of the multi-linear models
plot(lm$residuals)
abline(0,0, col = "red")
#(b) Check the residuals of each predictor
par(mfrow = c(2,3))
plot(lm1$residuals)
plot(lm2$residuals)
plot(lm3$residuals)
plot(lm4$residuals)
plot(lm5$residuals)
plot(lm6$residuals)
plot(lm7$residuals)
```
#Uncorrelated error
```{r}
library("car", lib.loc="/Library/Frameworks/R.framework/Versions/3.3/Resources/library")
durbinWatsonTest(lm)
```
# remedial measures: log data transformation
```{r}
lm11 = lm(log(medv)~crim,data)
lm22 = lm(log(medv)~zn,data)
lm33 = lm(log(medv)~indus,data)
lm44 = lm(log(medv)~nox,data)
lm55 = lm(log(medv)~rm,data)
lm66 = lm(log(medv)~age,data)
lm77 = lm(log(medv)~tax,data)
par(mfrow = c(2,3))
plot(lm11$residuals)
plot(lm22$residuals)
plot(lm33$residuals)
plot(lm44$residuals)
plot(lm55$residuals)
plot(lm66$residuals)
plot(lm77$residuals)
```
3. use least median square method do linear regression
```{r}
lm_median<-lmsreg(medv ~ crim+zn+indus+nox+rm+age+tax, data=Boston)
lm_median

```